Minimum Viable Products (MVP) has seen a rapid rise in popularity, and it is
now one of the most popular to take on new projects that present a risk.
MVP is a set of guidelines for creating a product which focuses on validating
a product idea with customers early in the development lifecycle, it normally
contains enough features and functionalities to be usable and setup a ground
for the development of a product for later stages. And relies on early adopters
to help the product reach its full potential. However, opting for such an approach,
can be turn into a heavy load on the development team, if development keeps on expanding
on the product without opting to set a strong foundation to be strongly maintainable.

One way to tackle that is to opt for adapting the MVP to industrial standards,
turning it into a SaaS product. The industrial standards are a set of norms that
are set by the industry to have a strong foundation for the development of a
product, to be able to be easily maintained and allow to turn the MVP into more of
an actually rigid solution. For example, taking one of the most popular and famous
companies in the world, Amazon, the industry standard for software development. The main
idea of the project was selling books online and that started with a minimalistic operated
online store rather than a full fledged e-commerce store. Just to make sure that
the idea is properly tested on the market, then it have been industrialized to match
a fully built online books store with a strong foundation, which later turned out to
be a full on e-commerce not store but rather a infrastructure.

In the course of my graduation project, I present report is a brief overview of adapting
parts of the MVP foundation to industrial norms. On the basis of this, we will be able to
see how the MVP can be adapted to the industry standards, and how it can be used to create
a SaaS product that can be more secure, more reliable and easily maintained.

Through the course of this report, we will be introducing the context of the project,
the problem that's we're facing and the solutions that we're going to propose and implement
to solve them.

