For the contributions, we had multiple subjects and points within the solution touched on,
which as follow:
\begin{itemize}
    \item Persistence Layer: Which took interest in the implementation of an archival 
        system for the solution, it went in two different ways:
        \begin{itemize}
            \item Implementing the archival for general data that was in JSON format.
            \item Implementing the archival for data that was binary files such as PDFs.
        \end{itemize}
    \item Security Layer: It was the part where we implemented a new filter to the backend,
        specifically for limiting the call backs to the API, through a rate limiter.
        And next was the authentication, which was a migration from a simple Bearer token
        transactional method to a more secure method based on Http Only Cookies storage for
        the token.
    \item Infrastructure: This part mainly targetted, migrating the environment from linux
        virtual machines to managed containers that could offer a better scalability,
        in terms of managing peak load for requests and memory usage.
    \item Continuous integration: Here we implemented a CI/CD pipeline for the solution,
        which took advantage of the previously implemented containerized environment.
        To make the deployment more streamlined and efficient, to allow for easier hot
        fixes and upgrades, and force a better testing of the solution before allowing 
        code to be deployed in an automated fashion.
    \item Refactoring: This was the last point, where the main goal here is to make
        the code more readable and easier to maintain. The trade off is that it will
        take a long time to implement as it requires implementation of a lot of tests
        for the old code. To allow for the beginning of the re-implementation of the
        code, to a newer version that relies on a different architecture.
\end{itemize}

\newpage

\section{Introduction}

So with the context, the problematic and the scope of the project setup, it's 
time to pass to the contributions phase, which consists of conceptual contributions
and their implementation. To be more precise, we'll be handling persistence layer,
security layer, the infrastructure layer and a new deployment strategy.

For each of these layers and phases, we'll be starting with a conceptual or theoretic
study of the solutions we have, and then we'll be talking about the implementation 
projecting it to the project to finally move to the testing and how it was done to validate
the solution used.

\section{Target}\label{sec:target-comp}
\input{target_comp.tex}

\section {Persistence layer}

For the database we had two subjects to study:
\begin{itemize}
        \item Databases for archival purposes
        \item Databases for storing files
    \end{itemize}

\subsection {Archival Database}
\input{archival.tex}

\subsection {File storage Database}
\input{fileStorage.tex}

\section {Security and Authentication}

\subsection {Ratelimiting} \label{subsec:ratelimiting}
\input{ratelimiting.tex}

\subsection {Authentication}
\input{auth.tex}

\section {Containerization and Deployment}
\input{containerization.tex}

\section {Continuous Integration}
\input{ci.tex}

\section {Refactoring and Improvements}\label{sec:refactoring}
\input{refactoring.tex}

\section {Conclusion}

To conclude, during the implementation of the subjects, we had implemented a lot of
new features and improvements ranging from databases and security, to infrastructure 
and deployment.
As we've seen during the last section \ref{sec:refactoring}, the refactoring wasn't 
implemented yet, but the main goal of this phase has been discussed in such a way
that it will be easier to implement the refactoring in the future.
The main goal of this contributions phase was to make the ground work for a more rigid
and upgradable solution, which would allow for the development of a more robust and
upgradable solution once the refactoring is fully implemented.

